Computational methods in landscape ecology

### 2024-05-20 Sections/spatial-patterns.qmd
adds various comments

@@

## Landscape Mosaic
<!-- Bosch -->

>>>>

spatial patterns definitions in the literature (general)
?existance of spatial pattterns in many contexts, from geography, through biology and urban planning to medical studies
?relation of spatial patterns to spatial processes

spatial patterns in data (computational approach); its limitations and considerations
raster data
vector data: point, line, polygon
point clouds 
time series data

one variable vs. multivariable spatial patterns
categorical vs. continuous spatial patterns

resolution, scale, and extent in spatial patterns

short intro to the subsequent sections

!to conclusions that relation of spatial patterns to spatial processes is a golden grail of landscape ecology
!what with fractals?
!ai and deep learning still seems to be underused in landscape ecology

@@

intro to entropy
various concepts: thermodynamic (Boltzmann), information (Shannon), Kolmogorov, etc.
how they are related to each other
how they are related to spatial patterns and landscape ecology

entropy measures are still related to the underlining data representation

claims of relations between entropy and thermodynamics

## Landscape mosaic
<!-- Bosch -->

an intro to the section
what is similar to landscape metrics

add an info about shape metrics
